Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-15 Paper2015.tex
Work in progress.

% Paper 2015

\documentclass[12pt,journal]{IEEEtran}

@@

\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}} 	% Article title

@@

In simulation work, more components such as bending magnet, shielding, target surroundings, collimator, and detector system were constructed compare with preliminary model of neutron source at the ANITA neutron facility at TSL, see Fig.~\ref{fig:ANITAoverview}. 
The detector system includes five size simulated-detectors which are placed at different positions, see Table~\ref{table:DetectorSystem}.

@@

\begin{table}[!tbp]
	\caption{Detector system}
	\label{table:DetectorSystem}
	\centering
	\begin{tabular}{lllr}
	\toprule
	Detector name & Size   & Location from Target & Ref \\
		  	   & $cm$ & $cm$			& 	\\
	\midrule
	CUP		& $60\times60\times0.1$  & $75.0$    & \cite{Prokofiev14}\\
	CUPTOF	& $60\times60\times0.1$  & $84.0$    & \cite{Prokofiev14}\\
	FF 		& $120\times240\times0.1$  & $86.6$    & \\
	TE 		& aperture size  & $186.7$  & \\
	SUP  		& $120\times120\times0.1$  & $250.0$  & \cite{Prokofiev2009}\\
	\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!tbp]
\caption{Neutron yield under the umbra region at the standard user position}	%title of the table
	\label{table:NYieldRadiusEffectAtSUP}
	\centering
	\begin{tabular}{l c c c}
            \toprule
            {collimator}   &{$< \SI{1}{\MeV}$}	&{$\geq 1 \& <\SI{10}{\MeV}$}	&{$\geq \SI{10}{\MeV}$}\\
            \cmidrule(r){2-4}
            {\si{\centi\metre}}     &	&{\SI{1e-6}{ncm^{-2}p^{-1}}}	&\\
             \midrule
		3 		& 0.833 	& 0.975	& 0.525\\
		10.2 		& 1.394 	& 1.248	& 0.525\\ 
		30 		& 1.962 	& 1.555	& 0.650\\
            \bottomrule
	\end{tabular}
\end{table}

@@

@@

\begin{table}[!tbp]
\caption[{$\gamma$ yield for each collimator in a radius of \SI{5}{\cm} at the CUP}]{$\gamma$ yield for each collimator at the CUP}	%title of the table
\centering
\label{table:GYieldCUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}  \\ 
\cmidrule(r){2-3}
\SI{}{\cm}       & \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-6}.\gamma.cm^{-2}.p^{-1}}\\
\hline % insert single-line
3 & 4.93 & 15.73\\

@@

\begin{table}[!tbp]
\caption[$\gamma$ yield for each collimator in umbra region at the SUP]{$\gamma$ yield for each collimator in umbra region at the SUP}	%title of the table
\centering
\label{table:GYieldSUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}   \\ 
\cmidrule(r){2-3}
\SI{}{\cm}       & \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}} &  \SI{}{10^{-7}.\gamma.cm^{-2}.p^{-1}}\\
\hline % insert single-line
3 & 2.3 & 6.7\\

@@

>>>>

% Paper 2015
\documentclass[12pt,journal]{IEEEtran}

@@

\usepackage{siunitx}
\DeclareSIUnit\photon{\ensuremath{\gamma}}
\DeclareSIUnit\proton{p}
\DeclareSIUnit\neutron{n}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

\usepackage{todo}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\title{Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL}

@@

A detailed model of the ANITA geometry was implemented in Geant4.
This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
The target is cooled by water and surrounded by a stainless-steel cooling jacket.
The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).

@@

Simulations were conducted using Geant4 version~TBD.
The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.
In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several locations.
In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre (check centre)~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.
The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

\begin{table}[!tbp]
\caption{Neutron yield under the umbra region at the standard user position}	%title of the table
	\label{table:NYieldRadiusEffectAtSUP}
	\centering
	\begin{tabular}{l c c c}
		\toprule
          {collimator}   		&{$< \SI{1}{\MeV}$}	&{$\geq 1 \& <\SI{10}{\MeV}$}	&{$\geq \SI{10}{\MeV}$}\\
          \cmidrule(r){2-4}
          {\si{\centi\metre}}	&						&{\SI{1e-6}{\neutron\per\cm\squared\per\proton}}	&\\
          \midrule
		3 		& 0.833 	& 0.975	& 0.525\\
		10.2 	& 1.394 	& 1.248	& 0.525\\
		30 		& 1.962 	& 1.555	& 0.650\\
           \bottomrule
	\end{tabular}
\end{table}

@@

In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
Part of the motivation for this work was to investigate whether improvements in the fidelity of the Geant4 model would lead to increased quantitative agreement.
Fig.~\ref{fig:SUPCollimator}

\begin{figure}
    \todo{}
    \caption{Neutron field at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
    \label{fig:SUPCollimator}
\end{figure}

\begin{figure}
    \todo{}
    \caption{Neutron profile at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
    \label{fig:SUPProfile}
\end{figure}

Fig.~\ref{fig:FirstComparison}\ldots

\begin{figure}
	\todo{Here we need figures showing the integral spectra on log-log plots and equilethargic spectra normalised to unit area above \SI{10}{\MeV}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:FirstComparison}
\end{figure}

@@

\begin{table}[!tbp]
\caption[{$\gamma$ yield for each collimator in a radius of \SI{5}{\cm} at the CUP}]{$\gamma$ yield for each collimator at the CUP}	%title of the table
\centering
\label{table:GYieldCUP}
\begin{tabular}{lcc}
	\hline% insert double-line
	Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}  \\
	\cmidrule(r){2-3}
/\si{\cm}       & /\SI{e-6}{\photon\per\cm\squared\per\proton} & /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
\hline % insert single-line
3 & 4.93 & 15.73\\

@@

\begin{table}[!tbp]
\caption[$\gamma$ yield for each collimator in umbra region at the SUP]{$\gamma$ yield for each collimator in umbra region at the SUP}	%title of the table
\centering
\label{table:GYieldSUP}
\begin{tabular}{l	c	c}
\hline% insert double-line
Collimator size   & above \SI{1}{\MeV}   &  above \SI{0.1}{\MeV}   \\
\cmidrule(r){2-3}
/\si{\cm}       & \/\SI{e-6}{\photon\per\cm\squared\per\proton} &  /\SI{e-6}{\photon\per\cm\squared\per\proton} \\
\hline % insert single-line
3 & 2.3 & 6.7\\

@@

\todos
